Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2017-04-27 teaching.tex
modify all by analysis for 4-player game

>>>>

\subsection{Players and Strategy Spaces}
We add the international community:
\begin{enumerate}
	\item Home government (G) chooses $S_G \in \left\{SQ,C\right\}$ where SQ means 'Status Quo' of unrecognized statehood and C means 'Cede' the issue of status and recognize the secessionists as an independent state.
	\item Secessionists (S) choose $S_S \in \left\{SQ,C\right\}$, same as for $G$ except when they Cede, they rejoin the home state.
	\item Patron state (P) chooses $p \in [0,\infty)$ to invest in the secessionists status quo payoffs
	\item \textbf{International community (C) chooses} $c \in [0,\infty)$ \textbf{ to invest in the secessionists payoffs from rejoining the home state}
\end{enumerate}

\vskip.3in
\subsection{Timing and Information}
The patron makes its investment. This investment is seen by all other players. \textbf{Then the international community makes its investment. This investment is seen by all other players.} Then the home government and secessions move simultaneously.

\vskip.5in
\subsection{Payoffs}
We add payoffs for the international community, and the international community's investment in the secessionists payoffs from ceding.
\begin{itemize}
	\item The payoffs after ($SQ,SQ$) are $-p,\bm{-c},3,0+p$
	\item The payoffs after ($SQ,C$) are $-10-p,\bm{5-c},5,1\bm{+c}$
	\item The payoffs after ($C,SQ$) are $3-p,\bm{-7-c},0,5+p$
	\item The payoffs after ($C,C$) are $-p,\bm{-c},3,0\bm{+c}$
\end{itemize}
